Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-08 SupportingInformation.Rmd
notes on Anolis and regenerated data from DendroPy 4.4.0

**bmr-contrasts.csv** : This contains the trait contrasts
from phylogenetically independent contrasts [@SukumaranH2010] 
of data reported by [@GenoudIM2017] on the basal metabolic rate (BMR)
and mass of mammals species.
Specifically, the "SELECT" BMR data in their database were used for
 those species for which data were available.
A phylogeny in NEXUS [@NEXUS] format was extracted from the 
 supplementary information of [@GenoudIM2017].
Version 4.3 of the DendroPy library [@SukumaranH2010] was used to calculate 
  phylogenetic independent contrasts.
For each contrast, the path length spanned by the contrast (sum of the branch
  lengths) and the contrast for the mass, BMR and natural
  logarithm of the mass were written as a row in the bmr-contrasts.csv file.

@@

**contrasts.csv** : Prof. M. T. Holder to add description here about this dataset.

>>>>

**bmr-contrasts.csv** : This contains the trait contrasts
from phylogenetically independent contrasts [@SukumaranH2010] 
of data reported by [@GenoudIM2017] on the basal metabolic rate (BMR)
and mass of mammals species.
Specifically, the "SELECT" BMR data in their database were used for
 those species for which data were available.
A phylogeny in NEXUS [@NEXUS] format was extracted from the 
 supplementary information of [@GenoudIM2017].
Version 4.4.0 of the DendroPy library [@SukumaranH2010] was used to calculate 
  phylogenetic independent contrasts using Python 2.7.
For each contrast, the path length spanned by the contrast (sum of the branch
  lengths) and the contrast for the mass, BMR and natural
  logarithm of the mass were written as a row in the bmr-contrasts.csv file.

@@

**contrasts.csv** : Raw data on measurements of anatomical
features of several species of *Anolis* lizards was downloaded
from the Dryad data package [@MahlerIRL2013Data] associated with
[@MahlerIRL2013].
The contrasts.csv file was produced by using version 4.4.0 of the DendroPy 
  library [@SukumaranH2010]  to calculate 
  phylogenetic independent contrasts on the the data in the GA_Anolis_traits.csv
  file of Mahler et at. using their maximum clade credibility tree (GA_Anolis_MCC.nex)
  as the phylogeny.
